D3064R0: Bringing the Laws of Physics, Computer-System Constraints, and Compilers to Bear on the OOTA Problem

### 2024-01-11 ootavacuous.tex
January 11, 2024 title change
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>
Yet another title change and sdep definition adjustment
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

\begin{document}
\title{D3064R0: Bringing the Laws of Physics to Bear on the OOTA Problem}

@@

The manual analysis uses the informal rule that a semantic dependency
exists between a set of relaxed atomic loads\footnote{
	Please see
	Appendix~\ref{app:Non-Trivial Semantic Dependencies}
	for examples showing why this is a set of loads rather than a
	single load.}
and a store on any execution where different values loaded would change
the address stored to, the value stored, or the whether or not that store
would be executed in the first place, with the proviso that stores of
the same value to the same address having the same ordering properties
are fungible.

>>>>

\begin{document}
\title{D3064R0: Bringing the Laws of Physics, Computer-System Constraints, and Compilers to Bear on the OOTA Problem}

@@

The manual analysis uses the informal rule that a semantic dependency
exists between a set of relaxed atomic loads\footnote{
	Please see
	Appendix~\ref{app:Non-Trivial Semantic Dependencies}
	for examples showing why this is a set of loads rather than a
	single load.}
and a store on any execution where different values loaded would change
the address stored to, the value stored, or the number of times that
store would be executed, with the proviso that stores of the same value
to the same address having the same ordering properties are fungible.
